---
title             : |
  How effective are interventions designed to help people detect misinformation? \
  A Pre-data Collection Registration
shorttitle        : "A Meta-Analysis of Misinformation Interventions"
header-includes:  | # to prevent floats from moving past certain points (for the appendix)
  \usepackage{placeins} 
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
author: 
    
  - name          : "Jan Pfänder"
    affiliation   : "1"
  - name          : "Sacha Altay"
    affiliation   : "2"
    corresponding : yes    # Define only one corresponding author
    email         : "sacha.altay@gmail.com"
    address       : ""
affiliation:
  - id            : "1"
    institution   : "Institut Jean Nicod, Département d’études cognitives, ENS, EHESS, PSL University, CNRS, France"
  - id            : "2"
    institution   : "Department of Political Science, University of Zurich, Switzerland"
authornote: |
  JP received funding from the SCALUP ANR grant ANR-21-CE28-0016-01
  SA received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation program (grant agreement nr. 883121).
abstract: |
  
  
  In recent years, many studies have proposed individual-level interventions to reduce people's susceptibility for believing in misinformation. Researchers have typically evaluated the effectiveness of these interventions based on a discernment measure--how much more participants rate true news as accurate than false news. Here, we will re-assess the findings of this literature by analyzing their data using a Signal Detection Theory (SDT) framework. This allows us to differentiate between two different kinds of intervention effects: First, the effect on sensitivity, which is the ability of discriminating between true and false news that researchers typically look for. Second, the effect on response bias, which is the extent to which participants become generally more/less skeptical in their accuracy ratings for all news (whether true or false). We run an Individual Participant Data meta-analysis (IPD) based on a sample of studies that we identified via a systematic literature review following the PRISMA guidelines. We use a two-stage approach: First, we extract individual participant data and run a Signal Detection Theory analysis separately for each experiment. Second, we run a meta-analysis on the experiment-level outcomes.
keywords          : "Misinformation; fake news; false news; news judgment; news accuracy; news discernment"
csl               : nature.csl
floatsintext      : yes
linenumbers       : no 
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
output: 
  papaja::apa6_docx: default
  bookdown::html_document2:
    toc: true
    toc_depth: 2
    number_sections: true
    theme: cerulean
    df_print: paged
  papaja::apa6_pdf: 
    keep_tex: true
always_allow_html: true
appendix:
  - "registration_step-by-step-SDT.Rmd"
bibliography: references.bib
---

```{r packages, message=FALSE, warning=FALSE}
# load required packages
library("lme4")        # model specification / estimation
library("lmerTest")    # provides p-values in the output
library("tidyverse")   # data wrangling and visualisation
library("afex")        # anova and deriving p-values from lmer
library("broom")       # extracting data from model fits 
library("broom.mixed") # using tidy() for mixed models
library("metafor")     # doing mata analysis
library("kableExtra")  # for tables
```

```{r setup, include=FALSE}
# Figure out output format
is_docx <- knitr::pandoc_to("docx") | knitr::pandoc_to("odt")
is_latex <- knitr::pandoc_to("latex")
is_html <- knitr::pandoc_to("html")

# Word-specific things
table_format <- ifelse(is_docx, "huxtable", "kableExtra")  # Huxtable tables
conditional_dpi <- ifelse(is_docx, 300, 300)  # Higher DPI
conditional_align <- ifelse(is_docx, "default", "center")  # Word doesn't support align

# Knitr options
knitr::opts_chunk$set(
  echo = TRUE, warning = FALSE, message = FALSE,
  # tidy.opts = list(width.cutoff = 120),  # Code width
  # fig.retina = 3, dpi = conditional_dpi,
  # fig.width = 7, fig.asp = 0.618,
  # fig.align = conditional_align, out.width = "100%",
  fig.path = "output/figures/",
  cache.path = "output/_cache/",
  fig.process = function(x) {  # Remove "-1" from figure names
    x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
    if (file.rename(x, x2)) x2 else x
  },
  options(scipen = 99999999)  # Prevent scientific notation
)

# R options
options(
  width = 90,  # Output width
  dplyr.summarise.inform = FALSE,  # Turn off dplyr's summarize() auto messages
  knitr.kable.NA = "",  # Make NAs blank in kables
  kableExtra.latex.load_packages = FALSE,  # Don't add LaTeX preamble stuff
  modelsummary_factory_default = table_format,  # Set modelsummary backend
  modelsummary_format_numeric_latex = "plain"  # Don't use siunitx
)
```

```{r functions}
# load plot theme
source("functions/plot_theme.R") 

# load other functions
source("functions/own_functions.R")
```

```{r, include=FALSE, message=FALSE}
# load individual_level data
data <- read_csv("data/simulations/individual_level.csv")
```

# Introduction

In recent years, many studies have tested interventions designed to help people detect online misinformation. In these studies, researchers have typically evaluated the effectiveness of interventions based on a discernment measure--how much more participants rate true news as accurate than false news.

This measure, although widely used, has been criticized recently [@guayHowThinkWhether2023; @highamMeanRatingDifference2024a; @gawronskiSignaldetectionFrameworkMisinformation2024]. For example, @modirrousta-galianGamifiedInoculationInterventions2023 re-analyzed data on gamified interventions--Bad News and Go Viral!--previously shown by researchers to increase people's news discernment. While the original studies used a discernment measure based on mean differences, @modirrousta-galianGamifiedInoculationInterventions2023 used a SDT framework. They show that the interventions have in fact not improved participant's ability to discriminate between true and false news, but have increased general skepticism, i.e. a tendency to respond 'not accurate' to all news items, including the true ones. This suggests that some interventions designed to 'inoculate' people against misinformation, might not be as effective as previously thought. They might even be counterproductive in a context where the vast majority of news people encounter are true news.

Here, our aim is to extend this work and systematically re-evaluate misinformation interventions. We focus on all kinds of individual-level interventions designed to reduce people's susceptibility for believing in misinformation. We use Signal Detection Theory (SDT) to differentiate between two different effects of interventions: First, the effect on sensitivity, which is the ability of discriminating between true and false news that researchers typically look for. Second, the effect on response bias, which is the extent to which participants shift their general response criterion, i.e. the extent to which they become generally more/less skeptical in their accuracy ratings for all news (whether true or false). 

We formulate two main research questions: How do interventions against misinformation affect: (i) people's ability to discriminate between true and false news (sensitivity, or "d'", in a SDT framework; RQ1)?, and (ii) people's skepticism towards news in general (i.e. response bias, or "c", in a SDT framework; RQ2)?

We will also test some moderator effects. At this stage, we know that we will ask the following questions: Do the effects of the interventions (both on sensitivity and response bias) differ between (i) different types of interventions; (ii) politically concordant and politically discordant news; (iii) different age groups? It is likely that after data collection, we will have a better overview of variables and would want to ask more moderator questions. If that is the case, we will specify these moderators in a second pre-registration before analysis.

In order to compare it to our results, we will try to descriptively assess how many studies originally reported positive effects of their intervention on news discernment. At this point, it is hard to predict how comparable the orginial authors' evaluation will be with ours, e.g. due to different co-variates in the original models. If after data collection we deem it feasible, we will provide an overview for how many experiments our re-evaluation does (or does not) confirm increased sensitivity.

We will do an [Individual Participant Data meta-analysis (IPD)](https://training.cochrane.org/handbook/current/chapter-26), using a two-stage approach: First, we extract individual participant data from relevant studies and run a Signal Detection Theory analysis separately for each experiment. Second, we run a meta-analysis on the outcomes.

# Methods

## Data/Sampling

### Systematic Literature review

We will base ourselves on the systematic literature review of a recent meta-analysis on people's accuracy judgments of true and false news [@pfanderSpottingFalseNews2024]. Of all the studies extracted from this review, we will reduce our sample to those that tested an intervention to augment news discernment.

Since the field is rapidly growing, we will also try to add papers that have been published since the systematic review. We will code for all papers whether they were part of the original systematic review of @pfanderSpottingFalseNews2024 or identified afterwards, so that the selection process is transparent. In a second pre-registration–after data collection but before analysis–we will publish a full list of studies, detailing whether they were part of the systematic review or added afterwards by us because we came across them.

We have already stored individual level data for several studies used in @pfanderSpottingFalseNews2024. We have yet to collect data for the remaining studies. For the studies that we have already stored individual-level data, we have not yet cleaned it according to the requirements of the study proposed here. We have not performed any of the here suggested analysis on the collected data. We have simulated data to be clear on the data structure our analysis requires and to test how well our model performs in recovering parameters. All analyses presented in this pre-registration use this simulated data.

### Selecting Interventions

Sometimes, within the same experiment, researchers test different interventions, by comparing it to a single control group. For a meta-analysis, this is a problem, [sometimes referred to as double-counting](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#unit-of-analysis). The correlations due to the same comparison group cannot be accounted for by a meta-analytic model [@harrer2021]. Following options recommended in the [cochrane manual](https://training.cochrane.org/handbook/current/chapter-23#section-23-3) we use the following rule of thumb: If the interventions are conceptually similar enough, pool the interventions together. If they are too dissimilar, pick the most pertinent one.

It is hard to predict in advance how relevant these decisions will be. However, we will make them on a purely theoretical basis: Once we have collected our data, we will make an overview of all interventions, and make a decision in case of multiple intervention arms within the same experiment. We will preregister these decisions as part of the second pre-registration. Only then will we run the analysis.

We have tried to mimic the situation of multiple intervention groups but only one control group in our simulated data. Some experiments have several interventions, and they are sometimes conceptually similar, sometimes different. Table \@ref(tab:intervention-selection-a) shows the experimental structure of the first two simulated papers.

```{r intervention-selection-a}
data %>% 
  filter(paper_id %in% c(1:2)) %>% 
  distinct(paper_id, experiment_id, intervention_id, intervention_type) %>% 
  kable(caption = "Experimental structure of the first two simulated papers",
        booktabs = TRUE) %>% 
    kable_styling(font_size = 10) 
```

In Paper 1, there are two experiments (experiment_id = '1' and experiment_id = '2'). Both experiments only have two arms, respectively: the control group and an intervention group (priming for Experiment 1; warning labels for Experiment 2). In these cases, since there is only one intervention, there is no decision to make as to which intervention to keep. By contrast, the first experiment of Paper 2 has three arms, among with two different intervention types ('priming' and 'warning labels'). In such a case, we would need to make a decision on which intervention type to keep. This decision will probably depend on which intervention type occurred how many times etc.

In our data, we will first detect all experiments with multiple interventions (Table \@ref(tab:intervention-selection-b))

```{r intervention-selection-b}
conflict <- data %>% 
  distinct(paper_id, experiment_id, unique_experiment_id, intervention_id, intervention_type) %>% 
  group_by(unique_experiment_id) %>% 
  # substact 1 because of the control condition
  summarize(n_different_intervention_types = n_distinct(intervention_type) - 1, 
            # display different intervention types
            types = paste(unique(intervention_type), collapse = ", ")
            ) %>% 
  # label all experiments with more than one intervention type
  mutate(conflict = ifelse(n_different_intervention_types > 1, TRUE, FALSE)) %>% 
  filter(conflict == TRUE)

conflict %>% 
  kable(caption = "Studies with mutliple intervention arms in the simulated data", 
        booktabs = TRUE) %>% 
    kable_styling(font_size = 10) 
```

We will then have to make specific exclusion decisions for each experiment.

```{r}
conflict <- conflict %>% 
  # list all intervention types to be excluded for a given experiment
  mutate(exclude =   case_when(unique_experiment_id == "1_1" ~ "priming, warning labels",
                               unique_experiment_id == "10_1" ~ "priming",
                               unique_experiment_id == "10_3" ~ "warning labels",
                               # continue this list for all studies (we don't do this here because lazy)
                               TRUE ~ NA_character_
  )
  ) %>% 
  select(unique_experiment_id, exclude)

conflict %>% 
  kable(caption = "Example of exclusion decisions for some of the experiments with multiple intervention arms", 
        booktabs = TRUE) %>% 
    kable_styling(font_size = 10) 
```

We then filter our data to only keep the intervention conditions we decided upon.

```{r}
data <- data %>% 
  left_join(conflict) %>% 
  # Use str_detect to check if intervention_type is found in exclude string
  filter(is.na(exclude) | !str_detect(exclude, intervention_type))

# check
# data %>%
#   distinct(paper_id, experiment_id, unique_experiment_id, intervention_id, intervention_type, condition) %>%
#   filter(unique_experiment_id %in% c("10_1", "2_1", "5_1"))
```

Once all decisions regarding the intervention selections have been made, we can rely our 'condition' variable for all models below, which takes only the values of either 'control' or 'intervention'.

## Analysis plan

### Outcomes

We want to measure the effects of misinformation interventions on two outcomes of Signal Detection Theory (SDT): $d'$ ("d prime", sensitivity), and $c$ (response bias). Table \@ref(tab:sdt-vocabulary) shows how instances of news ratings map onto SDT terminology.

```{r sdt-vocabulary}
# Data
table_data <- tibble(
  Stimulus = c("True news (target)","False news (distractor)"),
  Accurate = c("Hit", "False alarm"),
  `Not Accurate` = c("Miss", "Correct rejection")
)

# Set Stimulus as row names
# rownames(table_data) <- table_data$Stimulus
# table_data$Stimulus <- NULL

# Create table using kable
kable(table_data, 
      caption = "Accuracy ratings in Signal Detection Theory terms", 
              booktabs = TRUE) %>%
  kable_paper(full_width = FALSE) %>%
  add_header_above(c(" ", "Response" = 2))
```

```{r}
# make SDT variables
sdt_data <- data %>% 
  # code ratings in terms of SDT language
  mutate(sdt_outcome = case_when(accuracy == 1 & veracity == "true" ~ "hit", 
                                 accuracy == 1 & veracity == "fake" ~ "false_alarm",
                                 accuracy == 0 & veracity == "true" ~ "miss",
                                 accuracy == 0 & veracity == "fake" ~ "correct_rejection",
                                 .default =  NA)
         )
```


The sensitivity, $d’$, measures people's capacity to discriminate between true and false news. It is defined as the difference of the standardized hit and false alarm rates

$$
d' = \Phi^{-1}(HR) - \Phi^{-1}(FAR) 
$$

where $HR$ refers to hit rate or the proportion of true news trials that participants classified--correctly--as "accurate" ($HR = \frac{N_{Hits}}{N_{Hits} + N_{Misses}}$), $FAR$ refers to false alarm rate or the proportion of false news trials that participants classified--incorrectly--as "accurate" ($HR = \frac{N_{False Alarms}}{N_{FalseAlarms} + N_{Correct Rejections}}$). $\Phi$ is the cumulative normal density function, and is used to convert z scores into probabilities. Its inverse, $\Phi^{-1}$, converts a proportion (such as a hit rate or false alarm rate) into a z score. Below, we refer to standardized hit and false alarm rates as zHR and zFAR, respectively. Due to this transformation, a proportion of .5 is converted to a z score of 0 (reflecting responses at chance). Proportions greater than .5 produce positive z scores, and proportions smaller than .5 negative ones. A positive $d'$ score indicates that people rate true news as more accurate than false news. 

The response bias, $c$ can be conceived of as an overall tendency to rate items as accurate. It is defined as

$$
c = -\frac{1}{2}(\text{zHR} + \text{zFAR})
$$

Note that $c$ = 0 when $zFAR = -zHR$. Because $-zHR = z(1-HR)$ is the (z-transformed) share of misses (true news rated as "not accurate"), $c$ = 0 when the false alarm rate is equal to the rate of misses (Macmillan & Creelman (2004). In other words, if people--mistakenly--rate true news as not accurate (the rate of misses) as much as they--mistakenly--rate false false news as accurate (the rate of false alarms), then there is no response bias. A positive $c$ score occurs when the miss rate (rating true news news as false) is larger than the false alarm rate (rating false news as true). In other words, a positive $c$ score indicates that people were more skeptical towards true news than they were gullible towards false news. We refer to this as an overall tendency towards skepticism. 

Our outcome of interest is the intervention effects on $d'$ ("d prime", sensitivity) and $c$ (response bias). Since these outcomes are about the difference between the control and the treatment group, we call them "Delta". Specifically, they are defined as:

$$
\Delta d' = d'_{treatment} - d'_{control}
$$

and

$$
\Delta c = c_{treatment} - c_{control}.
$$

A positive $\Delta d'$ score indicates that the intervention increased participants' ability to discriminate between true and false news compared to the control group. A positive $\Delta c$ score indicates that the intervention led to a greater tendency towards skepticism, meaning participants were more likely to rate items as "not accurate" regardless of veracity, compared to the control group. 

### Variables

Table \@ref(tab:codebook) contains a list of variables we will collect. We might not be able to collect all variables for all studies. For political concordance, e.g., this will certainly not be the case. 

```{r codebook}
# Create the codebook data frame
codebook <- data.frame(
  Variable_Name = c(
    "paper_id", "experiment_id", "subject_id", "country", "year", 
    "veracity", "condition", "intervention_label", "intervention_description", 
    "accuracy_raw", "scale", "originally_identified_treatment_effect", 
    "concordance", "age", "identified_via", "id", 
    "unique_experiment_id", "accuracy"
  ),
  Description = c(
    "Identifier for each paper",
    "Identifier for each experiment within a paper",
    "Identifier of individual participants within an experiment",
    "The country of the sample",
    "Ideally year of data collection, otherwise year of publication",
    "Identifying false and true news items",
    "Treatment vs. control",
    "A label for what the intervention consisted of",
    "A detailed description of the intervention",
    "Participants' accuracy ratings on the scale used in the original study",
    "The scale used in the original study",
    "Whether the authors identified a significant treatment effect (`FALSE` if no, `TRUE` if yes)",
    "Political concordance of news items (concordant or discordant)",
    "Participant age",
    "Indicates if a paper was identified by the systematic review or added after",
    "Unique participant ID (merged `paper_id`, `experiment_id`, `subject_id`)",
    "Unique experiment ID (merged `paper_id` and `experiment_id`)",
    "Binary version of `accuracy_raw`; unchanged if originally binary"
  )
)

# Generate the styled table with kableExtra
kable(codebook, 
      caption = "Codebook for variables to collect",
      col.names = c("Variable Name", "Description"),
      booktabs = TRUE,
      longtable = TRUE,) %>%
  kable_styling(latex_options = "repeat_header",
                font_size = 10) %>% 
  column_spec(1, bold = TRUE) %>%  # Bold the first column
  column_spec(2, width = "25em") %>%  # Set width for the description column
  row_spec(0, bold = TRUE)  # Bold the header row
```

Building a comparable accuracy measure that we can analyze in the SDT framework outlined here, requires collapsing scales. The studies that we will look at use a variety of scales. Some use a binary scale, which is the one that is the most straightforward to use in a SDT framework (signal vs. no signal) and thus also the one we have simulated. However, a lot of studies use Likert-type scales. For these studies, we will collapse the original scores into a dichotomized version with answers of either 'accurate' (0) or 'not accurate' (1). For example, a study might have used a 4-point scale going from 1, not accurate at all, to 4, completely accurate. In this case, we will code responses of 1 and 2 as not accurate (0) and 3 and 4 as accurate (1). For scales, with a mid-point (example 3 on a 5-point scale), we will code midpoint answers as 'NA', meaning they will be excluded from the analysis.

### Main Analysis

We will run a participant-level meta analysis using a two-stage approach: First, for each experiment, we calculate a generalized linear mixed model (glmm) that yields SDT outcomes. The resulting estimates are our effect sizes. Second, we run a meta analysis on these effect sizes. In Appendix \@ref(step-by-step) to this registration, we explain step by step how to go from a by-hand SDT analysis to a glmm SDT analysis. In the following, we will outline the analysis steps we will perform. 

#### Stage 1: experiment-level analysis

For each experiment, we run a separate participant-level SDT analysis. Because participants provide several ratings, we use mixed-models with random participant effects that account for the resulting dependency in the data points. We use random effects both for the intercept and the effect of veracity. We do not use random effects for condition or the interaction of condition and veracity, as condition is typically manipulated between participants. We can obtain SDT outcomes directly from a generalized linear mixed model (glmm) when using a probit link function (see Appendix \@ref(step-by-step)). Table \@ref(tab:example-outcome-exp1) shows the model output for our simulated Experiment 1, from paper 1.

```{r}
# calculate model function
calculate_model <- function(data) {
  
  time <- system.time({
    model <- glmer(accuracy ~ veracity_numeric + condition_numeric + 
                     veracity_numeric*condition_numeric +
                     (1 + veracity_numeric | unique_subject_id),
                   data = data, 
                   family = binomial(link = "probit")
    )
  })
  
  time <- round(time[3]/60, digits = 2)
  
  # get a tidy version
  model <- tidy(model, conf.int = TRUE) %>% 
    # add time
    mutate(time_minutes = time)
  
  return(model)
  
}
# test
# mixed_model <- calculate_model(data %>% filter(unique_experiment_id == "1_1"))
# mixed_model
```

We calculate one model per experiment and store the results in a common data frame.

```{r}
# Running this model takes some time. We therefor stored the results in a data frame that we can reload. 
filename <- "data/simulations/models_by_experiment.csv" 

run_loop <- function(data, filename){
  
  # only execute the following if the file does NOT exist
  if (!file.exists(filename)) {
    
    # make a vector with all unique experiment ids
    experiments <- data %>% 
      distinct(unique_experiment_id) %>% 
      # slice(1:3) %>% # to test loop
      pull()
    
    time <- system.time({
      
      # run one model per experiment and store the results in a common data frame
      results <- experiments %>%
        map_dfr(function(x) {
          
          # restrict data to only the respective experiment
          experiment <- data %>% filter(unique_experiment_id == x)
          
          # extract paper id
          paper_id <- unique(experiment$paper_id)
          
          # To keep track of progress
          print(paste("calculating model for experiment ", x))
          
          model_experiment <- calculate_model(experiment) %>%
            mutate(unique_experiment_id = x,
                   paper_id = paper_id)
          
          return(model_experiment)
        })
    })
    
    write_csv(results, filename)
    
    print(paste("Elapsed time: ", round(time[3]/60, digits = 2), " minutes"))
  }
  
}

# execute function
run_loop(data, filename)

# read saved model results
model_results <- read_csv(filename)
```

We code our binary independent variables, veracity and condition, using deviation coding (i.e. for veracity, false = -0.5, true = 0.5; for condition, control = -0.5, treatment = 0.5). Using deviation coding, the main effect model output terms translate to SDT outcomes as follows: 

-   `(Intercept)` = average -$c$, pooled across all conditions
-   `veracity_numeric` = average $d'$, pooled across all conditions
-   `condition_numeric` = -$\Delta c$, i.e. the change in -response bias between control and treatment
-   `veracity_numeric:condition_numeric` = $\Delta d'$, i.e. the change in sensitivity between control and treatment

```{r}
# We clean up the model output by naming our estimates of interest in terms of SDT outcomes, and reversing the coefficients for response bias c, and delta response bias c.

model_results <- model_results %>% 
  filter(effect == "fixed") %>% 
  mutate(
    # make sdt outcomes
    SDT_term = case_when(
    term == "(Intercept)" ~ "average c",
    term == "veracity_numeric" ~ "average d'",
    term == "condition_numeric" ~ "delta c",
    term == "veracity_numeric:condition_numeric" ~ "delta d'",
    TRUE ~ "Other"
  ), 
  # reverse c and delta c estimates
  SDT_estimate = ifelse(term == "(Intercept)" | term == "condition_numeric", 
                        -1*estimate, estimate),
    sampling_variance = std.error^2
  ) 
```


```{r example-outcome-exp1}
model_results %>% 
  filter(unique_experiment_id == "1_1") %>% 
  select(-starts_with("conf")) %>% 
  rounded_numbers() %>% 
  select(-c(effect, group)) %>% 
  kable(
    caption = "Results of a generalize linear mixed model (glmm)",
    booktabs = TRUE) %>%
  kable_styling(font_size = 8,  # Set a smaller font size
                latex_options = c("scale_down")) # Scale down the table
```


As shown in Figure \@ref(fig:distributions), we can then plot the distributions of our outcome estimates of interest, across experiments. 

(ref:distributions) Distributions of Signal Detection Theory outcomes across experiments. Note that these distributions are purely descriptive - effect sizes are not weighted by sample size of the respective experiment, as they are in the meta-analysis. 

```{r distributions, fig.cap="(ref:distributions)"}
# make plot
ggplot(model_results, aes(x = estimate, fill = SDT_term)) +
  geom_density(alpha = 0.5, adjust = 1.5) +
  # colors 
  scale_fill_viridis_d(option = "inferno", begin = 0.1, end = 0.9) +
  # labels and scales
  labs(x = "z-Score", y = "Density") +
  guides(fill = FALSE, color = FALSE) +
  plot_theme +
  theme(strip.text = element_text(size = 14)) +
  facet_wrap(~SDT_term)
```

#### Stage 2: Meta-analysis

Next, we run a meta analysis on these effect size estimates at the experiment-level. In our models for the meta analysis, each effect size is weighted by the inverse of its standard error, thereby giving more weight to experiments with larger sample sizes. We will use random effects models, which assume that there is not only one true effect size but a distribution of true effect sizes. We will use a multi-level meta-analytic model, with random effects at the publication and the experiment level. This approach allows us to account for the hierarchical structure of our data, in which (at least some) papers (level three) contribute several effect sizes from different experiments (level two)^[Level 1 being the the participant level, i.e. the sampling variation of the original studies, see @harrer2021.]. However, the multi-level models do not account for dependencies in sampling error. When one paper contributes several effect sizes, one might expect their respective sampling errors to be correlated. To account for dependency in sampling errors, we compute cluster-robust standard errors, confidence intervals, and statistical tests for all meta-analytic estimates. For our simulated data, Table \@ref(tab:meta-model-results) shows the results of the meta-analytic models and Figure \@ref(fig:forest) provides an overview of effect sizes for each experiment as a forest plot. 

```{r}
# Function to calculate meta models
calculate_models <- function(data, yi, vi, robust = TRUE) {
  
  # provide metafor compatible names
  metafor_data <- data %>% 
    rename(yi = {{yi}}, 
           vi = {{vi}})
  
  # Multilevel random effect model for accuracy
  model <-  metafor::rma.mv(yi, vi, random = ~ 1 | paper_id / unique_experiment_id, 
                            data = metafor_data)
  
  return(model)
  
  if(robust == TRUE) {
    # with robust standard errors clustered at the paper level 
    robust_model <- robust(model, cluster = data$paper_id)
    
    return(robust_model)
  }
}
```

```{r meta-model-results}
# model for delta dprime
delta_dprime <- calculate_models(data = model_results %>% 
                                   filter(SDT_term == "delta d'"), yi = SDT_estimate, 
                                 vi = sampling_variance, robust = TRUE)

# model for delta c
delta_c <- calculate_models(data = model_results %>% 
                                   filter(SDT_term == "delta c"), yi = SDT_estimate, 
                                 vi = sampling_variance, robust = TRUE)


modelsummary::modelsummary(list("Delta d'" = delta_dprime, 
                                "Delta c" = delta_c
                                ), 
                           title = "Results of Meta-analysis",
                           stars = TRUE, 
                           output = "kableExtra"
                           )
```

(ref:forest) *Forest plots for delta d' and delta c*. The figure displays all effect sizes for both outcomes. Effects are weighed by their sample size. Effect sizes are z-values. Horizontal bars represent 95% confidence intervals. The average estimate is the result of a multilevel meta model with clustered standard errors at the sample level.

```{r forest, fig.cap="(ref:forest)"}
# Set up a 1x2 layout for the two plots
par(mfrow = c(1, 2))

# Calculate weights (e.g., inverse of standard error)
model_results <- model_results %>%
  mutate(weight = 1 / sqrt(sampling_variance))

# Create plot for d'
forest.rma(delta_dprime,
           xlim = c(-1, 2),          # Adjust horizontal plot region limits
           at = c(-1, -0.5, 0, 1, 2), 
           order = "obs",            # Order by size of yi
           slab = unique_experiment_id, 
           annotate = TRUE,          # Study labels and annotations
           efac = c(0, 1),           # Remove vertical bars at end of CIs
           pch = 15,                 # Change point symbol to filled squares
           col = "gray40",           # Change color of points/CIs
           cex.lab = 0.8, 
           cex.axis = 0.8,           # Increase size of x-axis title/labels
           lty = c("solid", "dotted", "blank"),  # Remove horizontal line at top of plot
           mlab = "BLASt", 
           ylim = c(-2, n_distinct(model_results$unique_experiment_id)), 
           addfit = FALSE, 
           xlab = "Delta d'") 
addpoly(delta_dprime, mlab = " ", cex = 1, row = -2) 
abline(h = 0)

# Create plot for c
forest.rma(delta_c,
           xlim = c(-1, 2),          # Adjust horizontal plot region limits
           at = c(-1, -0.5, 0, 1, 2), 
           order = "obs",            # Order by size of yi
           slab = unique_experiment_id, 
           annotate = TRUE,          # Study labels and annotations
           efac = c(0, 1),           # Remove vertical bars at end of CIs
           pch = 15,                 # Change point symbol to filled squares
           col = "gray40",           # Change color of points/CIs
           cex.lab = 0.8, 
           cex.axis = 0.8,           # Increase size of x-axis title/labels
           lty = c("solid", "dotted", "blank"),  # Remove horizontal line at top of plot
           mlab = "BLASt", 
           ylim = c(-2, n_distinct(model_results$unique_experiment_id)), 
           addfit = FALSE, 
           xlab = "Delta c") 
addpoly(delta_c, mlab = " ", cex = 1, row = -2) 
abline(h = 0)

# Reset the layout to the default (1x1)
par(mfrow = c(1, 1))

```

### Moderator analysis

We distinguish between two broad kinds of moderator variables: those that vary within-experiments (e.g. political concordance) and those that vary between experiments (e.g. intervention type). We will use different approaches for these two kinds.

#### a. within-experiment variables

There are two moderator variables that vary within-experiments that we will test: age and political concordance. Age varies within experiments, but between participants (each participant can only have one age). Political concordance varies not only within experiments, and also within participants--in the typical experiment design, each participant is shown both concordant and discordant items. In the text, we will focus on political concordance, which requires slightly more complex modelling, but provide the models for age in the respective code chunks. 

We have two options: (i) integrating political concordance in our baseline model. While this would be the straightforward thing to do, it involves a three-way interaction with many random effects and will likely bring up convergence issues; (ii) run our baseline model separately for concordant and discordant items. Then, proceed just as for between-experiment moderators.

##### i. Integrating Concordance in baseline model

In the first option, we add political concordance to our Stage 1 model, such that we have a three-way interaction between veracity, condition and political concordance.

```{r}
# calculate model function for political concordance
calculate_concordance_model <- function(data) {
  
  time <- system.time({
    model <- glmer(accuracy ~ veracity_numeric + condition_numeric + concordance_numeric + 
                     veracity_numeric*condition_numeric*concordance_numeric +
                     (1 + veracity_numeric + veracity_numeric:concordance_numeric | 
                        unique_subject_id),
                   data = data, 
                   family = binomial(link = "probit")
    )
  })
  
  time <- round(time[3]/60, digits = 2)
  
  # get a tidy version
  model <- tidy(model, conf.int = TRUE) %>% 
    # add time
    mutate(time_minutes = time)
  
  return(model)
  
}

# calculate model function for age
calculate_age_model <- function(data) {
  
  time <- system.time({
    model <- glmer(accuracy ~ veracity_numeric + condition_numeric + age + 
                     veracity_numeric*condition_numeric*age +
                     (1 + veracity_numeric  | 
                        unique_subject_id),
                   data = data, 
                   family = binomial(link = "probit")
    )
  })
  
  time <- round(time[3]/60, digits = 2)
  
  # get a tidy version
  model <- tidy(model, conf.int = TRUE) %>% 
    # add time
    mutate(time_minutes = time)
  
  return(model)
  
}
# age_model <- calculate_age_model(data %>% filter(unique_experiment_id == "1_1"))
# age_model %>% print(n = 14)
```

Table \@ref(tab:glmm-example-experiment1) illustrates the model output for the first experiment (Experiment 1 of Paper 1) in our simulated data.

```{r glmm-example-experiment1}
# test
concordance_model <- calculate_concordance_model(data %>% filter(unique_experiment_id == "1_1"))
concordance_model %>% 
  rounded_numbers() %>% 
  select(-c(effect, group)) %>% 
  kable(booktabs = TRUE, 
        caption = "Results of the generalized linear mixed model (glmm) on the first experiment (Experiment 1 of Paper 1) in our simulated data.") %>%
  kable_styling(font_size = 8,  # Set a smaller font size
                latex_options = c("scale_down")) # Scale down the table
```

Given that all our binary variables in the data are deviation-coded (-0.5 vs. 0.5) outputs are to be interpreted as follows:

Due to our coding for the two independent variables, the coefficients have the following interpretation:

-   `(Intercept)` = average -$c$, pooled across all conditions
-   `veracity_numeric` = average $d'$, pooled across all conditions
-   `condition_numeric` = -$\Delta c_{\text{condition}}$, i.e. the change in -response bias between control and treatment, pooled across concordant and discordant items
-   `concordance_numeric` = -$\Delta c_{\text{concordance}}$, i.e. the change in -response bias between concordant and discordant items, pooled across control and treatment
-   `veracity_numeric:condition_numeric` = $\Delta d'_{\text{condition}}$, i.e. the change in sensitivity between control and treatment, pooled across concordant and discordant items
-   `veracity_numeric:concordance_numeric` = $\Delta d'_{\text{concordance}}$, i.e. the change in sensitivity between concordant and discordant items, pooled across control and treatment
-   `condition_numeric:concordance_numeric` = Effect of concordance on -$\Delta c_{\text{condition}}$,
-   `veracity_numeric:condition_numeric:concordance_numeric` = Effect of concordance on $\Delta d'_{\text{condition}}$

Since interpretation can get a bit complex in three-way interactions [here is a good ressource](https://psyteachr.github.io/stat-models-v1/interactions.html#the-key-coding-schemes), we demonstrate below that the model estimates correspond to their respective SDT outcomes.

To do so, we first run the same model as before, on the same data as before (Experiment 1 of Paper 1), but removing the random effects, so that our model estimates will correspond to the estimates from a by-hand Signal Detection Theory analysis (Table \@ref(tab:glm-example-experiment1)).

```{r glm-example-experiment1}
# same model as above, but without random effects 
glm_model <- glm(accuracy ~ veracity_numeric + condition_numeric + concordance_numeric + 
                     veracity_numeric*condition_numeric*concordance_numeric,
                   data = data %>% filter(unique_experiment_id == "1_1"), 
                   family = binomial(link = "probit"))

# give nicer names to estimates
glm_model <- glm_model %>% 
  tidy() %>% 
  mutate(
    # reverse c and delta c estimates
    SDT_estimate = ifelse(term == "(Intercept)" | term == "condition_numeric" | term == "concordance_numeric" | term == "condition_numeric:concordance_numeric" , 
                      -1*estimate, estimate),
    SDT_term = case_when(term == "(Intercept)" ~ "average response bias (c)", 
                     term == "veracity_numeric" ~ "average sensitivity (d')", 
                     term == "condition_numeric" ~ "delta c (condition)",
                     term == "concordance_numeric" ~ "delta c (concordance)",
                     term == "veracity_numeric:condition_numeric" ~ "delta d' (condition)",
                     term == "veracity_numeric:concordance_numeric" ~ "delta d' (concordance)",
                     term == "condition_numeric:concordance_numeric" ~ "effect of concordance on delta c (condition)",
                     term == "veracity_numeric:condition_numeric:concordance_numeric" ~ "effect of concordance on delta d' (condition)",
    )
  ) 


glm_model %>% 
  rounded_numbers() %>% 
  kable(booktabs = TRUE, 
        caption = "Results of the generalized linear model (glm), i.e. without random effects, on the first experiment (Experiment 1 of Paper 1) in our simulated data.") %>%
  kable_styling(font_size = 8,  # Set a smaller font size
                latex_options = c("scale_down")) # Scale down the table
```

We can calculate the Signal Detection Theory outcomes by hand as from the summary data shown in Table \@ref(tab:summary-SDT-data).

```{r summary-SDT-data}
# calculate SDT outcomes per condition
sdt_outcomes <- sdt_data %>%
  filter(unique_experiment_id == "1_1") %>% 
  group_by(sdt_outcome, condition, political_concordance) %>%
  count() %>% 
  pivot_wider(names_from = sdt_outcome, 
              values_from = n) %>% 
  mutate(
    z_hit_rate = qnorm(hit / (hit + miss)),
    z_false_alarm_rate = qnorm(false_alarm / (false_alarm + correct_rejection)),
    dprime = z_hit_rate - z_false_alarm_rate,
    c = -1 * (z_hit_rate + z_false_alarm_rate) / 2
  ) %>% 
  ungroup() 

sdt_outcomes %>% 
  kable(booktabs = TRUE, 
        caption = "Summary data grouped by experimental condition for (Experiment 1 of Paper 1) in our simulated data.") %>%
  kable_styling(font_size = 8,  # Set a smaller font size
                latex_options = c("scale_down")) # Scale down the table

```

Based on this data, we can calculate the average response bias (`(Intercept)`) and sensitivity (`veracity_numeric`), pooled across all conditions; our treatment effects `delta_dprime` (`veracity_numeric:condition_numeric` in the model output) and `delta_c` (`condition_numeric` in the model output) from before, i.e. ignoring/pooling across political concordance; the differences in response bias (`concordance_numeric` in the model output) and sensitivity (`veracity_numeric:concordance_numeric` in the model output) between concordant and discordant items, pooling across control and treatment groups; the moderator effect of convergence on our original treatment effects `delta_dprime` and `delta_c`, i.e. how much stronger/weaker the effects on response bias (`condition_numeric:concordance_numeric` in the model output) and sensitivity (`veracity_numeric:condition_numeric:concordance_numeric` in the model output) are for concordant items, compared to discordant ones. Table \@ref(tab:moderator-SDT-by-hand) shows the results of these by-hand calculations. Comparing the results from the by-hand calculation (Table \@ref(tab:moderator-SDT-by-hand)) and the glm (Table \@ref(tab:glm-example-experiment1)), we note that the results are the same. 

```{r calculate-moderator-SDT-by-hand}
# average dprime and c
SDT_pooled_averages <- sdt_outcomes %>% 
  summarize(across(c(dprime, c), ~mean(.x, na.rm = TRUE), .names = "average_{.col}")) 

# treatment effect (i.e. main outcomes)
intervention_effects <- sdt_outcomes %>%
  select(political_concordance, condition, dprime, c) %>% 
  pivot_wider(
    names_from = condition, 
    values_from = c(dprime, c)
  ) %>% 
  mutate(delta_dprime = dprime_intervention - dprime_control, 
         delta_c = c_intervention - c_control) %>% 
  # pool across concordance
  summarize(across(starts_with("delta"), ~mean(.x, na.rm = TRUE), .names = "{.col}")) 

# differences in SDT outcomes by convergence
differences_SDT_by_convergence <- sdt_outcomes %>%
  select(political_concordance, condition, dprime, c) %>% 
  pivot_wider(
    names_from = political_concordance, 
    values_from = c(dprime, c)
  ) %>% 
  mutate(delta_dprime = dprime_concordant - dprime_discordant, 
         delta_c = c_concordant - c_discordant) %>% 
  # pool across condition
  summarize(across(starts_with("delta"), ~mean(.x, na.rm = TRUE), .names = "{.col}_concordance")) 

# moderator effects
moderator_effects <- sdt_outcomes %>%
  select(political_concordance, condition, dprime, c) %>% 
  pivot_wider(
    names_from = condition, 
    values_from = c(dprime, c)
  ) %>% 
  mutate(delta_dprime = dprime_intervention - dprime_control, 
         delta_c = c_intervention - c_control) %>% 
  select(political_concordance, starts_with("delta")) %>% 
  pivot_wider(
    names_from = political_concordance, 
    values_from = starts_with("delta")
  ) %>% 
  mutate(moderator_effect_dprime = delta_dprime_concordant - delta_dprime_discordant, 
         moderator_effect_c = delta_c_concordant - delta_c_discordant) %>% 
  select(starts_with("moderator"))

```

```{r moderator-SDT-by-hand}
# make an overview table 
SDT_outcomes_overview <- bind_cols(SDT_pooled_averages, intervention_effects, 
                                   differences_SDT_by_convergence, 
                                   moderator_effects) %>% 
  pivot_longer(
    cols = everything(), 
    names_to = "Outcome",
    values_to = "Value"
  ) %>% 
  rounded_numbers()

SDT_outcomes_overview %>% 
  kable(booktabs = TRUE, 
        caption = "Outcomes from by-hand SDT calculation.") %>%
  kable_styling(font_size = 10,  # Set a smaller font size
                latex_options = c("scale_down")) # Scale down the table
```

Just as we do for our main analysis, we estimate the model for each experiment separately and store the results in a common data frame.

```{r}
# Since the loop takes some time, we stored the results in a data frame that we can reload. 
filename <- "data/simulations/concordance_models.csv" 

run_loop_concordance <- function(data, filename){
  
  # make a vector with all unique experiment ids
  experiments <- data %>% 
    distinct(unique_experiment_id) %>% 
    #slice(1:10) %>% # reduce number of experiments here, to avoid long computation times
    pull()
  
  # only execute the following if the file does NOT exist
  if (!file.exists(filename)) {
    
    time <- system.time({
      
      # run one model per experiment and store the results in a common data frame
      results <- experiments %>%
        map_dfr(function(x) {
          
          # restrict data to only the respective experiment
          experiment <- data %>% filter(unique_experiment_id == x)
          
          # extract paper id
          paper_id <- unique(experiment$paper_id)
          
          # To keep track of progress
          print(paste("calculating model for experiment ", x))
          
          model_experiment <- calculate_concordance_model(experiment) %>%
            mutate(unique_experiment_id = x,
                   paper_id = paper_id)
          
          return(model_experiment)
        })
    })
    
    write_csv(results, filename)
    
    print(paste("Elapsed time: ", round(time[3]/60, digits = 2), " minutes"))
  }
  
}

# execute function
run_loop_concordance(data, filename)
# read saved model results
concordance_model_results <- read_csv(filename)
```

```{r}
# give nicer names to estimates
concordance_model_results <- concordance_model_results %>% 
  filter(effect == "fixed") %>% 
  mutate(
    # reverse c and delta c estimates
    SDT_estimate = ifelse(term == "(Intercept)" | term == "condition_numeric" | term == "concordance_numeric" | term == "condition_numeric:concordance_numeric", 
                      -1*estimate, estimate),
    SDT_term = case_when(term == "(Intercept)" ~ "average response bias (c)", 
                     term == "veracity_numeric" ~ "average sensitivity (d')", 
                     term == "condition_numeric" ~ "delta c (condition)",
                     term == "concordance_numeric" ~ "delta c (concordance)",
                     term == "veracity_numeric:condition_numeric" ~ "delta d' (condition)",
                     term == "veracity_numeric:concordance_numeric" ~ "delta d' (concordance)",
                     term == "condition_numeric:concordance_numeric" ~ "effect of concordance on delta c (condition)",
                     term == "veracity_numeric:condition_numeric:concordance_numeric" ~ "effect of concordance on delta d' (condition)",
    ),
    sampling_variance = std.error^2
  ) 
```

We then run the same meta-analytic model as for the main analysis, but on the moderator effect estimates. Table \@ref(tab:concordance-individual-level) shows the results of these models.

```{r concordance-individual-level}
# model for delta dprime
concordance_delta_dprime <- calculate_models(data = concordance_model_results %>% 
                                   filter(SDT_term == "effect of concordance on delta d' (condition)"), 
                                 yi = SDT_estimate, 
                                 vi = sampling_variance, robust = TRUE)

# model for delta c
concordance_delta_c <- calculate_models(data = concordance_model_results %>% 
                                   filter(SDT_term == "effect of concordance on delta c (condition)"), 
                                 yi = SDT_estimate, 
                                 vi = sampling_variance, robust = TRUE)


modelsummary::modelsummary(list("Delta d'" = concordance_delta_dprime, 
                                "Delta c" = concordance_delta_c
                                ), 
                           title = "Moderator analysis for politicial concordance based on an individual-level estimates",
                           stars = TRUE,
                           output = "kableExtra",
                           coef_rename = c("overall" = "Effect of political concordance")
                           ) 
```

##### ii. Running separate baseline models for concordance

If we encounter serious convergence issues by integrating the moderator variable in the individual-level model, we will use an alternative strategy. It consists in calculating separate models for concordant and discordant items, and then running a meta-regressions.

```{r}
# make two data frames for the two conditions
data_concordant <- data %>% filter(political_concordance == "concordant")
data_discordant <- data %>% filter(political_concordance == "discordant")

run_loop(data = data_concordant, filename = "data/simulations/concordant_data.csv")
run_loop(data = data_discordant, filename = "data/simulations/discordant_data.csv")

# read saved model results
concordant_results <- read_csv("data/simulations/concordant_data.csv")
discordant_results <- read_csv("data/simulations/discordant_data.csv")

results <- bind_rows(concordant_results %>% 
                       mutate(political_concordance = "concordant"), 
                     discordant_results %>% 
                       mutate(political_concordance = "discordant")
                     )

```

This procedure is basically the same as for between-experiment variables (see next section) and run a meta-regression, but there is a slight difference in the meta-regression model specifications: In the case of political concordance, our outcome data frame on which we run the meta-analysis contains two observations per experiment–one for discordant, the other for concordant items. We want to account for this dependency structure with a slightly different random effects structure, where observations are nested in experiments.

Table \@ref(tab:concordance-separate-baseline-model) shows the outcome of this meta-regression based on separate baseline estimates for concordant and discordant news items. In our simulated data--where no true moderator effect was modeled--these estimates are larger than the once we obtain from the intregrated individual-level model (Table \@ref(tab:concordance-individual-level)), but reassuringly they are not significant in either case.

```{r}
# add an observation identifier
results <- results %>% 
  mutate(observation_id = 1:nrow(.))
```

```{r}
# give nicer names to estimates
results <- results %>% 
  filter(effect == "fixed") %>% 
  mutate(
    # reverse c and delta c estimates
    SDT_estimate = ifelse(term == "(Intercept)" | term == "condition_numeric", 
                      -1*estimate, estimate),
    SDT_term = case_when(term == "(Intercept)" ~ "average response bias (c)", 
                     term == "veracity_numeric" ~ "average sensitivity (d')", 
                     term == "condition_numeric" ~ "delta c",
                     term == "veracity_numeric:condition_numeric" ~ "delta d'",
    ),
    sampling_variance = std.error^2
  ) 
```

```{r}
# Function to calculate meta models for the concordance variable
meta_regression_concordance <- function(data, yi, vi, moderator, robust = TRUE) {
  
  # provide metafor compatible names
  metafor_data <- data %>% 
    rename(yi = {{yi}}, 
           vi = {{vi}}, 
           moderator = {{moderator}})
  
  # Multilevel random effect model for accuracy
  model <-  metafor::rma.mv(yi, vi, 
                            mods = ~moderator,
                            random = ~ 1 | unique_experiment_id / observation_id, 
                            data = metafor_data)
  
  return(model)
  
  if(robust == TRUE) {
    # with robust standard errors clustered at the paper level 
    robust_model <- robust(model, cluster = data$paper_id)
    
    return(robust_model)
  }
}

```

```{r concordance-separate-baseline-model}
concordance_delta_dprime <- meta_regression_concordance(data = results %>% 
                                                              filter(SDT_term == "delta d'"), 
                                                            yi = SDT_estimate, 
                                                            vi = sampling_variance, 
                                                            moderator = political_concordance,
                                                            robust = TRUE)

concordance_delta_c <- meta_regression_concordance(data = results %>% 
                                                              filter(SDT_term == "delta c"), 
                                                            yi = SDT_estimate, 
                                                            vi = sampling_variance, 
                                                            moderator = political_concordance,
                                                            robust = TRUE)

modelsummary::modelsummary(list("Delta d'" = concordance_delta_dprime, 
                                "Delta c" = concordance_delta_c
                                ), 
                           stars = TRUE,
                           title = "Moderator analysis for political concordance based on a meta-regression",
                           output = "kableExtra"
                           )
```


#### b. Between-experiment variables

The main between-experiment variable we will look at here is interventions type. In our simulated data, we made up three intervention types ("literacy tips", "priming", "warning labels"). We run a meta-regression, in which we add intervention type as a covariate to the meta-analytic model from the main analysis. The results of this analaysis in our simulated data--where no true moderator effect was modeled--can be found in Table \@ref(tab:intervention-type-moderator). 


```{r}
# we add the intervention types to the effect sizes data frame with the SDT outcomes

# get interventions of all experiments
data_intervention_types <- data %>% 
  group_by(unique_experiment_id) %>% 
  # Get all experiments
  reframe(intervention_type = unique(intervention_type)) 

# add intervention types to data
moderator_data <- left_join(model_results, data_intervention_types)
```

```{r}
# Function to calculate meta models
meta_regression <- function(data, yi, vi, moderator, robust = TRUE) {
  
  # provide metafor compatible names
  metafor_data <- data %>% 
    rename(yi = {{yi}}, 
           vi = {{vi}}, 
           moderator = {{moderator}})
  
  # Multilevel random effect model for accuracy
  model <-  metafor::rma.mv(yi, vi, 
                            mods = ~moderator,
                            random = ~ 1 | paper_id / unique_experiment_id, 
                            data = metafor_data)
  
  return(model)
  
  if(robust == TRUE) {
    # with robust standard errors clustered at the paper level 
    robust_model <- robust(model, cluster = data$paper_id)
    
    return(robust_model)
  }
}
```

```{r}
# meta-regression for delta dprime
interventiontype_delta_dprime <- meta_regression(data = moderator_data %>% 
                                  filter(SDT_term == "delta d'"), 
                                yi = estimate, 
                                vi = sampling_variance, 
                                moderator = intervention_type,
                                robust = TRUE)

# meta-regression for c
interventiontype_delta_c <- meta_regression(data = moderator_data %>% 
                                  filter(SDT_term == "delta c"), 
                                yi = estimate, 
                                vi = sampling_variance, 
                                moderator = intervention_type,
                                robust = TRUE)
```

```{r intervention-type-moderator}
modelsummary::modelsummary(list("Delta d'" = interventiontype_delta_dprime, 
                                "Delta c" = interventiontype_delta_c
                                ), 
                           stars = TRUE,
                           output = "kableExtra",
                           title = "Moderator analysis for intervention type"
                           )
```


## Sensitivity Analysis

```{r}
sensitivity_data <- read_csv("data/simulations/sensitivity_analysis.csv")
```

Since we are running a meta-analysis based on a systematic review, we cannot control the final sample size. To have rough estimate on the statistical power we anticipate our study to have, we ran a sensitivity analysis based on a simulation. For the simulation, we--conservatively--assumed that the meta-analysis sample will consist of 10 papers. We assumed that each paper has between 1 and 4 experiments, and each experiment can have between two and four experimental arms (one of which is always the control condition). For each experimental arm, we assumed a sample size of 100 participants. The number of experiments per paper and arms per experiments was chosen randomly for each study. We further assumed that participants always saw 5 true and 5 false news. For details about other parameter assumptions, see the parameter list specified above. Although our final sample of papers will probably have properties quite different from what we assumed here, we believe these assumptions are rather conservative. 

In our simulations, we varied the values (small = 0.2, medium = 0.5, large = 0.8) for the true effect sizes for d' and c in the data. For each combination of the two effect sizes, we run 100 iterations, i.e. 100 times we generate a different sample of 10 papers, and run our meta-analysis on that sample. The aim of the sensitivity analysis consists in checking how many of these 100 meta-analyses find a significant effect. The share of analyses that detect the true effect is the statistical power.

As shown in Figure \@ref(fig:sensitivity-dprime) for d' and in Figure \@ref(fig:sensitivity-c) for c, even for very small effect sizes (0.2), we find statistical power greater than 90%, given our assumptions. For d', the value of c does not appear to affect the statistical power. For c, a low d' (0.2) appears to yield slightly lower statistical power than a medium (0.5) or large (0.8) d.

```{r}
# specify significance
alpha <- 0.05

plot_data <- sensitivity_data %>% 
  mutate(significant = ifelse(p.value < alpha, TRUE, FALSE)) %>% 
  group_by(parameter_delta_d_prime, parameter_delta_c) %>% 
  summarise(power = mean(significant)) 
```

(ref:sensitivity-dprime) Results of sensitivity analysis for Delta d'. The plot shows the power curve, i.e. the share of statistically significant effects across 100 simulated meta-analyses for each pair of values of d' (x-axis) and c (color legend).

```{r sensitivity-dprime, fig.cap="(ref:sensitivity-dprime)"}
ggplot(plot_data, 
       aes(x = parameter_delta_d_prime, y = power, color = as.factor(parameter_delta_c))) +
  geom_point(size = 1.5, alpha = 1) +
  geom_line(size = 1, alpha = 0.3) + 
  # add a horizontal line at 90%, our power_threshold
  geom_hline(aes(yintercept = .9), linetype = 'dashed') + 
  # Prettify!
  theme_minimal() + 
  scale_colour_viridis_d(option = "plasma", begin = 0.4, end = 0.7) + 
  scale_y_continuous(labels = scales::percent) + 
  labs(x = 'True effect size', y = 'Power', 
       title = "Power Curve for Delta d'")
```

(ref:sensitivity-c) Results of sensitivity analysis for Delta c. The plot shows the power curve, i.e. the share of statistically significant effects across 100 simulated meta-analyses for each pair of values of c (x-axis) and d' (color legend).

```{r sensitivity-c, fig.cap="(ref:sensitivity-c)"}
# plot results
ggplot(plot_data, 
       aes(x = parameter_delta_c, y = power, color = as.factor(parameter_delta_d_prime))) +
  geom_point(size = 1.5, alpha = 0.5) +
  geom_line(size = 1, alpha = 0.3) + 
  # add a horizontal line at 90%, our power_threshold
  geom_hline(aes(yintercept = .9), linetype = 'dashed') + 
  # Prettify!
  theme_minimal() + 
  scale_colour_viridis_d(option = "plasma") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(x = 'True effect size', y = 'Power', 
       title = "Power Curve for Delta c")
```

## Parameter Recovery

Instead of only checking whether our models find a significant effect or not, we also descriptively check how well our model recovers the data generating parameters accros the different samples. 

As shown in Figure \@ref(fig:sensitivity-parameter-dprime) for d' and Figure \@ref(fig:sensitivity-parameter-c) for c, we find that the distributions of meta-analytic estimates across the 100 samples per pair of effect sizes are centered around the true data generating parameter when the effect size is small (0.2). With an increasing true effect size, however, the estiamte distributions tend to be shifted to the left of the parameter, which suggests that our models consistently underestimate the true effect. 

Overall, our simulation suggests that (i) given conservative sample size assumptions, we will have large enough statistical power to detect even small effects, and (ii) that our model might slightly underestimates true effect sizes, which makes it a conservative estimator.

(ref:sensitivity-parameter-dprime) Distributions of Delta d' across simulated meta-analyses. The plot shows the distribution of meta-analytic estimates, for each combination of Delta d' and Delta c values. 

```{r sensitivity-parameter-dprime, fig.cap="(ref:sensitivity-parameter-dprime)"}
# custom function for grid labels
custom_labeller <- labeller(
  parameter_delta_c = function(x) paste("Delta c:", x),
  parameter_delta_d_prime = function(x) paste("Delta d':", x)
)

# plot Delta d' estimates
ggplot(sensitivity_data %>% filter(term == "delta d'"), aes(x = estimate)) +
  geom_histogram() +
  geom_vline(aes(xintercept = parameter_delta_d_prime), linetype = "dotted", color = "black") +
  labs(x = "Estiamte for Delta d'") + 
  facet_grid(rows = vars(parameter_delta_c), cols = vars(parameter_delta_d_prime), 
    labeller = custom_labeller)
```

(ref:sensitivity-parameter-c) Distributions of Delta c across simulated meta-analyses. The plot shows the distribution of meta-analytic estimates, for each combination of Delta c and Delta d' values. 

```{r sensitivity-parameter-c, fig.cap="(ref:sensitivity-parameter-c)"}
ggplot(sensitivity_data %>% filter(term == "delta c"), aes(x = estimate)) +
  geom_histogram() +
  geom_vline(aes(xintercept = parameter_delta_c), linetype = "dotted", color = "black") +
  labs(x = "Estimate for Delta c") + 
  facet_grid(cols = vars(parameter_delta_c), rows = vars(parameter_delta_d_prime), 
    labeller = custom_labeller)
```

# Data availability

# Code availability


\FloatBarrier

# References

::: {#refs}
:::


\newpage

# (APPENDIX) Appendix {-}

```{r child = "registration_step-by-step-SDT.Rmd"}
```

